ODGI: understanding pangenome graphs

### 2021-11-04 manuscript/fig_extract_viz_draw_position_untangle.tex
update and squeeze

            \includegraphics[width=\linewidth, trim=0cm 0cm -10cm 0cm]{fig/extract_viz_draw_position_untangle/chr6_pan_fa_a2fb268_4030258_6a1ecc2_smooth_gfa_og_mhc_og_O_og_lay_H1000w100_png_svg}

>>>>

            \includegraphics[width=\linewidth, trim=0cm 10cm -19cm 0cm]{fig/extract_viz_draw_position_untangle/chr6_pan_fa_a2fb268_4030258_6a1ecc2_smooth_gfa_og_mhc_og_O_og_lay_H1000w100_png_svg}
